Data Exploration

### 2024-04-30 R/eda-code/exploratory-analysis.qmd

```{r}
#load needed packages. make sure they are installed.
library(here) #for data loading/saving
library(dplyr)
library(skimr)
library(ggplot2)
library(tidyr)
library(forcats)
```

@@

# save to file
summarytable_elife = here("results", "summarytable.rds")
saveRDS(explorfigdata, file = summarytable_elife)
```

>>>>

```{r}
#load needed packages. make sure they are installed.
library(here) #for data loading/saving
library(dplyr)
library(skimr)
library(ggplot2)
library(tidyr)
library(forcats)
library(gtsummary) #line added by Rachel for add_stat function to work
```

@@

```{r}
# save to file
summarytable_elife = here("results", "summarytable.rds")
saveRDS(explorfigdata, file = summarytable_elife)
```
